### 2025-06-06 paper/conclusion.tex
Update appendices

Our two-staged analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting. The discretization approach for continuous-time economic models treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities, providing computational implementation templates while preserving essential incentive structures. We constructed observed reward functions enabling reinforcement learning without direct reward signals and developed specialized transformer loss functions for Lévy process observations. Our implementation incorporates Graph Neural Networks with temporal and spatial attention mechanisms capturing network topology and temporal dependencies. We introduce theoretically grounded off-policy asymmetric analysis methods moving beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence. Despite these advances, catastrophic forgetting prevents direct measurement of predicted equilibrium strategies, requiring alternative analytical approaches, and computational complexity limits analysis to small networks and finite horizons, potentially missing asymptotic behaviors theoretical models emphasize.

>>>>

Our two-staged analysis methodology provides systematic approaches for extracting insights from multi-agent learning dynamics despite catastrophic forgetting. The discretization approach for continuous-time economic models treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities, providing computational implementation templates while preserving essential incentive structures. We constructed observed reward functions enabling reinforcement learning without direct reward signals and developed specialized transformer loss functions for Lévy process observations. Our implementation incorporates Graph Neural Networks with temporal and spatial attention mechanisms capturing network topology and temporal dependencies. We introduce theoretically grounded off-equilibrium asymmetric analysis methods moving beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence. Despite these advances, catastrophic forgetting prevents direct measurement of predicted equilibrium strategies, requiring alternative analytical approaches, and computational complexity limits analysis to small networks and finite horizons, potentially missing asymptotic behaviors theoretical models emphasize.

### 2025-06-06 paper/intro.tex
Update appendices

A key methodological innovation is our discretization approach for continuous-time economic models, which treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities. This provides computational implementation templates while preserving essential incentive structures from theoretical models. We construct observed reward functions that enable reinforcement learning without direct reward signals and develop specialized transformer loss functions for Lévy process observations. Our theoretically grounded off-policy asymmetric analysis methods move beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence—capabilities essential for understanding real-world social learning dynamics.

>>>>

A key methodological innovation is our discretization approach for continuous-time economic models, which treats Lévy processes through Euler-Maruyama schemes and maps continuous decisions to discrete action probabilities. This provides computational implementation templates while preserving essential incentive structures from theoretical models. We construct observed reward functions that enable reinforcement learning without direct reward signals and develop specialized transformer loss functions for Lévy process observations. Our theoretically grounded off-equilibrium asymmetric analysis methods move beyond symmetric equilibria analysis, allowing heterogeneous agent behaviors and asymmetric strategy convergence—capabilities essential for understanding real-world social learning dynamics.
